### 2020-01-27 Summary/Summary.tex
Story 182: Intro complete

\section{Summary - Ramp input}

@@

Simultaneous fast and accurate measurement is still a challenging and active problem in metrology.
A sensor is a dynamic system that produces a transient response.
For fast measurements, the unknown input needs to be estimated using the sensor transient response.
When a model of the sensor exists, standard compensation filter methods can be used to estimate the input.
If a model is not available, either an adaptive filter is used or a sensor model is identified before the input estimation. 
Recently, a signal processing method was proposed to avoid the identification stage and estimate directly the value of a step input from the sensor response.
This data-driven step input estimation method requires only the order of the sensor dynamics and the sensor static gain.
To validate the data-driven step input estimation method, in this paper, the uncertainty of the input estimate is studied and illustrated on simulation and real-life weighing measurements.
It was found that the predicted mean-squared error of the input estimate is close to an approximate Cram\'er-Rao lower bound for biased estimators.

>>>>

\vspace{-1.2cm}

Sensors are dynamical systems and the physical quantity is the input excitation.
To have fast measurements, the input must be estimated during the sensor transient state.
Otherwise, users have to wait for the sensor steady state when the response is proportional to the input through the sensor static gain.
One approach to get fast input estimation is filtering the sensor transient response with another dynamical system aiming to reconstruct the input and to compensate the estimation time.
Another approach is processing the transient response on a digital signal processor (DSP).
Compensators are model based and DSPs allow model free methods that can reduce the estimation time.

There exists a model-free method that directly estimates the step input level from the sensor step response.
This method was formulated as a Hankel structured errors-in-variables (EIV) problem where the regression matrix and the regressor are correlated.
The structured EIV problem is solved with recursive least-squares to allow real-time implementation.
The range of application of this step input estimation method is wide because it is independent from sensor models.

The stochastic properties of the step input estimation method are unknown and are not straightforwardly evident.
To validate the method for metrology applications, we studied the estimate uncertainty by doing a statistical analysis of the step input estimation.
The estimate uncertainty can be defined in terms of the estimate bias and variance.
The statistical analysis of the estimation method yields expressions that predict the estimate first and second moments.

We computed the Cram\'er-Rao bound of the structured EIV problem to determine the minimum theoretical variance of the estimate.
This bound was compared to the estimate mean squared error (MSE) in simulations and in experiments with temperature and weighing sensors.
It was found that the input estimation is biased but with small variance, and that the estimate MSE is less than one order of magnitude larger than the Cram\'er-Rao bound.
In the practice, the step input estimation method was found to be robust when the Gaussian and white measurement noise assumption was not satisfied.

\begin{comment}
\section{Summary - Ramp input}

@@

Simultaneous fast and accurate measurement is still a challenging and active problem in metrology.
A sensor is a dynamic system that produces a transient response.
For fast measurements, the unknown input needs to be estimated using the sensor transient response.
When a model of the sensor exists, standard compensation filter methods can be used to estimate the input.
If a model is not available, either an adaptive filter is used or a sensor model is identified before the input estimation. 
Recently, a signal processing method was proposed to avoid the identification stage and estimate directly the value of a step input from the sensor response.
This data-driven step input estimation method requires only the order of the sensor dynamics and the sensor static gain.
To validate the data-driven step input estimation method, in this paper, the uncertainty of the input estimate is studied and illustrated on simulation and real-life weighing measurements.
It was found that the predicted mean-squared error of the input estimate is close to an approximate Cram\'er-Rao lower bound for biased estimators.
\end{comment}

%\newpage
